---
title: "Reading Data Into R"
author: "Vivekanandan Srinivasan"
date: "9/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading in tomato data from url

```{r }
url <- "http://www.jaredlander.com/data/Tomato%20First.csv"
tomato <- read.table(file = url, header = TRUE, sep = ",")
head(tomato)
```

## Reading from databases

```{r}
require(RODBC)
# Create a connection to the database called "db"
db <- odbcConnect("DATABASE", uid="USERNAME", pwd="PASSWORD", believeNRows=FALSE)
# Check that connection is working (Optional)
odbcGetInfo(db)
```

## Running simple query in database

```{r}
# Simple SELECT * query from one table
ordersTable <- sqlQuery(db, "SELECT * FROM Orders", stringAsFactors=FALSE)
head(OrderTable)
```


## Joining Two Tables 

```{r}
# Do join between the two tables
query <- "SELECT * FROM Orders, [Order Details] where Orders.OrderID=[Order Details].OrderID
detailsJoin <- sqlQuery(db, query, stringAsFactors=FALSE)
```

## Saving R object to Rdata format



```{r}
save(tomato,file="tomato.rdata")
rm(tomato)
```

## Checking the deleted R object

```{r}
head(tomato)
```

## Reloading tomato data from Rdata

```{r}
load("tomato.rdata")
# Check if it exist now
head(tomato)
```


## Creating Multiple Data

```{r}
n <- 20
r <- 1:10
w <- data.frame(n,r)
head(w)
```

```{r}
save(n,r,w, file="multiple.rdata")
# delete them
rm(n,r,w)

```

```{r}
head(w)
```


```{r}
# now load them back from rdata
load("multiple.rdata")
n
r
```

## Loading data included with R ggplot2


```{r}
require(ggplot2)
data(diamonds)
head(diamonds)
```

## List of all data available in ggplot2 package

```{r}
data()
```

## Scraping table from online resource

```{r}
library(XML)
url <- "http://www.jaredlander.com/2012/02/another-kind-of-super-bowl-pool/"
bowlPool <- readHTMLTable(url, which=1, header=FALSE, stringAsFactors=FALSE)
bowlPool
```

## Installing aws.s3 package

```{r}
# latest stable version
install.packages('aws.s3', repos = c('cloudyr' = 'http://cloudyr.github.io/drat'))

# on windows you may need:
install.packages('aws.s3', repos = c('cloudyr' ='"http://cloudyr.github.io/drat'), INSTALL_opts = '--no-multiarch')
```

## Accessing s3 bucket

```{r}
Sys.setenv('AWS_ACCESS_KEY_ID' = 'XXXXXXXXX',
           'AWS_SECRET_ACCESS_KEY' = 'yyyyyyyy',
           'AWS_DEFAULT_REGION' = 'us-west-1')

library('aws.s3')
bucketlist()
# To get listing of all objects in a public bucket
files <- get_bucket(bucket = 'bucket name')
```

## Commonly used function to read and write objects in S3 

```{r}
# save an in-memory R object into S3
s3save(mtcars, bucket = 'my_bucket', object = 'mtcars.Rdata')

# `load()` R objects from the file
s3load('mtcars.Rdata', bucket = 'my_bucket')

# get file as raw vector
get_object('mtcars.Rdata', bucket = 'my_bucket')
# alternative 'S3 URI' syntax:
get_object('s3://my_bucket/mtcars.Rdata')

# save file locally
save_object('mtcars.Rdata', file = 'mtcars.Rdata', bucket = 'my_bucket')

# put local file into S3
put_object(file = 'mtcars.Rdata', object = 'mtcars2.Rdata', bucket = 'my_bucket')
```



